The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-09 rational.tex
some reminders and re-org
more shuffling and notes

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions in {{langRevEE}} }
\label{sec:monoidal-constructions}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions Specific to Negation}
\label{sec:neg-constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions Specific to Multiplication}

@@

For a traced monoidal category {{C}} the Int construction produces a
Compact Closed Category called Int {{C}} \cite{joyal1996traced}.
Further we know that the target of the Int construction is isomorphic
to the target of \G construction of Abramsky \cite{Abramsky96:0} from
Haghverdi. However, note that the {{langRevEE}} is not the same as the
image of the Int construction on {{langRevT}}, since the the later
lacks a multiplicative tensor that distributes over the additive tensor
in Int {{langRevT}}.

@@

@@

>>>>

\roshan{Can we cite away unification, reificatio, handling of
  substitutions etc?}

@@

\roshan{Talk about non-determinism, determinism and our handling of
  choices. Also, in what sense are we logically reversible?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions in {{langRevEE}} }
\label{sec:monoidal-constructions}

@@

Mention LL and {{a -o b}}.

@@

\roshan{Also: additive functions aren't values - they are
  possibilities. Multiplicative functions really are values.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions Specific to Negation}
\label{sec:neg-constructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constructions Specific to Multiplication}

@@

@@

\paragraph*{Logic Programming and Backtracking.} 
This is a constrained form of backtracking and a constrained form of
logic programming.

\paragraph*{Linear Logic and GoI.} 
Say something.

\paragraph*{Int Construction.}
For a traced monoidal category {{C}} the Int construction produces a
Compact Closed Category called Int {{C}} \cite{joyal1996traced}.
Further we know that the target of the Int construction is isomorphic
to the target of \G construction of Abramsky \cite{Abramsky96:0} from
Haghverdi. However, note that the {{langRevEE}} is not the same as the
image of the Int construction on {{langRevT}}, since the the later
lacks a multiplicative tensor that distributes over the additive
tensor in Int {{langRevT}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computing in the Field of Algebraic Numbers}
